Diagnoses and cell types

### 2025-10-09 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd

There are five library with an order of magnitude more reference than query cells; let's look more closely at the validation groups present to get a sense.

>>>>

There are five libraries with an order of magnitude more reference than query cells; let's look more closely at the validation groups present to get a sense.
